Standardization of ceramic shape: A case study from the Iron Age pottery from northeastern Taiwan

### 2020-08-20 analysis/paper/paper.Rmd
minor edit to intro

---
title: "Standardization of ceramic shape: A case studay from the Iron Age pottery from northeastern Taiwan"

@@

This research investigates if there was increasing ceramic specialization resulting from Indigenous interaction with Europeans in the 17th century or Chinese in the 19th century, two major foreign influences in early historical Taiwan, which may indicate social changes in Indigenous societies. We predict that competition within the Indigenous community at Kiwulan for foreign resources and trade partnerships with European or Chinese colonizers may have led to the emergence of craft specialization caused by greater economic and social control of ceramic production by a small group of individuals. Using standardization in ceramic shapes as a proxy for craft specialization, we ask: Did colonial trade impact the shape of locally-produced Indigenous pottery vessels? Did pottery shape become more statistically homogeneous after foreign contacts with European colonizers or Chinese immigrants?

>>>>

---
title: "Standardization of ceramic shape: A case study from the Iron Age pottery from northeastern Taiwan"

@@

This research investigates if there was increasing ceramic specialization resulting from Indigenous interaction with Europeans in the 17th century or Chinese in the 19th century, two major foreign influences in early historical Taiwan, which may indicate social changes in Indigenous societies. We predict that competition within the Indigenous community at Kiwulan for foreign resources and trade partnerships with European or Chinese colonizers may have led to the emergence of craft specialization caused by greater economic and social control of ceramic production by a small group of individuals. Using standardization in ceramic shapes as a proxy for craft specialization, we ask: Did colonial trade impact the shape of locally-produced Indigenous pottery vessels? Did pottery shape become more homogeneous after foreign contacts with European colonizers or Chinese immigrants?
